\vspace{-10mm}\bf \mytitle

### 2020-11-29 ms.Rnw
a few more small edits

<<debug,echo=F>>=
run_level <- 2
#run_level <- "jasa-sept-2020"
#run_level <- 2
bm_run_level <- run_level
#mscale_run_level <- run_level
mscale_run_level <- 3
slice_run_level <- run_level

>>>>

<<debug,echo=F>>=
run_level <- 1
#run_level <- 2
#run_level <- "jasa-sept-2020"
bm_run_level <- run_level
mscale_run_level <- run_level
slice_run_level <- run_level
